Smoothing seismicity techniques applied to seismic source characterization and probabilistic seismic hazard analysis in Brazil

### 2015-05-16 manuscript.tex
increasing biblio and finish comments + minor changes on the sec 2, data presentation.

Although the standard \citet{cornell_1968}-\citet{mcguire_1976} methodology often used to assess seismic hazard makes use of expert opinions to predefined seismogenic zones, one goal of this paper is to review a few smoothed seismicity methods based on \gls{kde} which results in a grid or a smoothed seismicity surface without define any seismic zone polygon (also known as \textit{zoneless} approaches).

@@

Figure \ref{fig_occurrence} presents the catalog \gls{mfd}. For the minimum magnitude the threshold was 2.9. The blue x and red crosses are the incremental and cumulative recurrence distributions binned by 0.2 magnitude unity. Stepp completeness table and \citet{bsb_2014} declustered catalogue was used. Also a fixed b-value (b=1) incremental distribution is shown in blue continuous line, and the fitted by maximum-likelihood method (magenta, $b=0.91\pm0.07$), \citet{weichert_1980} (green, $b=0.88\pm0.04$) and \citet{kijko_2012} (orange, $0.76\pm0.04$) are shown as continuous lines. The respective a-values was $3.7$, $3.8\pm0.2$, $3.5\pm0.2$, $3.2\pm0.1$. The minimum magnitude on that completeness table was 2.9.

COMMENT

@@

>>>>

Although the standard \citet{cornell_1968}-\citet{mcguire_1976} methodology often used to assess seismic hazard makes use of expert opinions to predefined seismogenic zones, one goal of this paper is to review a few smoothed seismicity methods \citep{riznichenko_1959} based on \gls{kde} which results in a grid or a smoothed seismicity surface without define any seismic zone polygon (also known as \textit{zoneless} approaches).

@@

@@

Figure \ref{fig_occurrence} presents the catalog \gls{mfd}. For the minimum magnitude threshold was 2.9. The blue exes and red crosses are the incremental and cumulative recurrence distributions binned by 0.2 magnitude unity. Stepp completeness (table \ref{tab:completeness_stepp}) and \citet{bsb_2014} declustered catalogue was used.

Simple \citet{gutenberg_richter_1944} incremental \glspl{mfd},
\begin{equation}
\log{N}(m|a,b) = a - b \times m,
\end{equation}
were fitted using a fixed $b$-value (b=1), showed as the blue continuous line (fig. \ref{fig_occurrence}), by the maximum-likelihood method (magenta, $b=0.91\pm0.07$), \citet{weichert_1980} (green, $b=0.88\pm0.04$) and \citet{kijko_2012} methods (orange, $b=0.76\pm0.04$) are shown as continuous lines. The respective $a$-values was $3.7$, $3.8\pm0.2$, $3.5\pm0.2$, $3.2\pm0.1$.

From these distributions over the incremental catalog data, its possible to note just few records with magnitudes greater than 5, even considering different magnitude completeness on time, due probably the small observation time (few than 100 years) on Brazil stable crustal set.

Other important feature extracted from figure \ref{fig_occurrence}, is the low values of the $b$-values relative to the unity. Incremental b=1 \gls{mfd} underestimate the earthquake occurrences, specially under great magnitudes. From now on, we will assume the $b$-value of 0.9 as better representative for the whole region. On the future more investigations on the spatial $b$-value variations should be undertaken.
